Twists of supersymmetric gauge theories

### 2020-01-08 paper.tex
4d

We will call $\alpha$ in a twisting datum a \defterm{twisting homomorphism}.
\brian{Is this quite right? I think $\alpha$ is something different.
Physics usually calls the twisting homomorphism the one from the Lorentz group to $G_R$. 
Also, I think $Q$ is required to be a scalar under the twisting homomorphism.}

@@

\begin{remark}
Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
where the $\ZZ/2$-grading on $E$ is the total grading.
\end{remark}

@@

We decompose the fields with respect to the subgroup $\SU(3) \sub \SO(6)$.  We can identify the two fundamental representations of $\SU(3)$ with $\Omega^{0,1}(\CC^3)$ and $\Omega^{1,0}(\CC^3)$. 
\begin{align*}
c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
\end{align*} 
and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.  In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
\begin{align*}
S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* + [\chi, A_0]\chi^* +A_0[B_{1,0}, A_0]\wedge B_{1,0}^* + \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\nu, A_0]\wedge \nu^* + [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^* + [\nu', A_0]\wedge \nu'^* \\
I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (B_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\nu', \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^3}6$.

@@

\subsection{$\cN=1$ with chiral multiplet matter}
There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
For concreteness, we will fix a nonzero supercharge of negative chirality $$Q = Q_- \in S_-$$ to twist by. 
Such supercharges are minimal (i.e. have two dimensional image).  
They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.

\begin{prop}[See also \cite{SWchar}]
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$. 
\end{prop}

>>>>

@@

\begin{remark}
Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
where the $\ZZ/2$-grading on $E$ is the total grading.
\end{remark}

@@

We decompose the fields with respect to the subgroup $\SU(3) \sub \SO(6)$.  We can identify the two fundamental representations of $\SU(3)$ with $\Omega^{0,1}(\CC^3)$ and $\Omega^{1,0}(\CC^3)$. 
\begin{align*}
c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
\end{align*} 
\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.  In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
\begin{align*}
S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* + [\chi, A_0]\chi^* +A_0[B_{1,0}, A_0]\wedge B_{1,0}^* + \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\nu, A_0]\wedge \nu^* + [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^* + [\nu', A_0]\wedge \nu'^* \\
I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (B_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\nu', \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^3}6$.

@@

\subsection{$\cN=1$ with chiral multiplet matter} 
There is a minimal supersymmetric field theory with $\cN=1$ supersymmetry consisting of a pure gauge theory coupled to supersymmetric matter depending on a complex representation $R$.

%The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.

The field content for the 4-dimensional $\cN=1$ super Yang-Mills theory coupled to chiral matter is given by:
\begin{itemize}
\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4 ; \fg)$.
\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^1(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
\item scalars: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
\item fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
\end{itemize}

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
Such supercharges are necessarily of rank $1$, and for concreteness we will fix a square-zero supercharge of negative chirality $$Q = Q_+ \in S_+$$ to twist by. 
Such supercharges are minimal (i.e. have two dimensional image).  
They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\begin{align*}
c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda_- & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda_+ & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) \\
\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R^*) \\
\Bar{\phi} & \mapsto \gamma_0 \in \Omega^{2,2}(\CC^2 ; R) \\
\psi_+ & \mapsto \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) \\
\psi_- & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R)
\end{align*}
and their antifields:
\begin{align*}
c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
\end{align*}

The untwisted action functionals decompose as follows.

\begin{align*}
S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (\lambda_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\lambda_0^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}4$.

\begin{prop}[See also \cite{SWchar}]
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$. 
\end{prop}

\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int \dvol  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int \dvol (\phi, \psi_0^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

The twisted theory is therefore perturbatively equivalent to the theory with BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \bigg( (B_{2,1} \ol \dd_{A_{0,1}} A_{0})  + B_{2,0} F_{0,2} + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1} + \beta_{2,1} \dbar_{A_{0,1}} \gamma_0 \\ 
  &\qquad  + [A_{0,2}, A_0]\wedge B_{2,0} + \frac{1}{2}[A_0, A_0]B_{2,2} +  [\gamma_0, A_0]\wedge \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1}  \bigg).
\end{align*}
This is indeed the action functional of the required theory, where $\lambda_{0,2}$ is identified as the antifield to $A_{0,1}$.
 \end{proof}
